The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-06 manuscript/manuscript.Rnw
fix spalax table references

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \textit{Nannospalax galili} are shown in
\cref{tab:top50_n_galili_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_n_galili_placenta}.

@@

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \textit{Sus scrofa} are shown in
\cref{tab:top50_pig_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_pig_placenta}.

>>>>

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \textit{Nannospalax galili} are shown in
\cref{tab:top50_n_galili_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_nannospalax_galili_placenta}.

@@

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \textit{Sus scrofa} are shown in
\cref{tab:top50_pig_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_sus_scrofa_placenta}.
